### 2017-03-30 paper.tex
Add link layer info

\newpage
\chapter{Introduction}
\label{sec:introduction}

\newpage
\chapter{Literature Review}
\label{sec:literature-review}

@@

\newpage
\chapter{Proposed Solution and Methodology}
\label{sec:methodology}

@@

@@

As stated in chapter \ref{sec:literature-review}, the United Kingdom's Office
of Communications restrict what frequencies can be used for airborne
radio transmissions, and how much power the transmissions can be sent at.
Those restrictions constrain what existing protocols can be used to transmit
arbitrary data over radio. This disqualifies existing packet radio protocols
that would have fulfilled most of the requirements, in use in other countries
like AX.25.

@@

\subsubsection{Forward Error Correction}

@@

\begin{center}
\begin{bytefield}{16}
    \bitheader{0,7,8,15} \\
    \begin{rightwordgroup}{Header}
        \bitbox{8}{01011010} & \bitbox{8}{version} \\
        \bitbox{16}{sequence number}
    \end{rightwordgroup} \\
    \begin{leftwordgroup}{Payload}
        \wordbox[lrt]{1}{data} \\
        \skippedwords \\
        \wordbox[lrb]{1}{}
    \end{leftwordgroup} \\
    \begin{rightwordgroup}{Error Correction}
        \wordbox[lrt]{1}{checksum} \\
        \skippedwords \\
        \wordbox[lrb]{1}{}
    \end{rightwordgroup}
\end{bytefield}
\end{center}

@@

\begin{center}
\begin{bytefield}{32}
    \bitheader{0,7,8,15,16,23,24,31} \\
    \begin{rightwordgroup}{Header}
        \bitbox{8}{version} & \bitbox{8}{payload ID} &
        \bitbox{16}{packet length} \\
        \bitbox{32}{latitude} \\
        \bitbox{32}{longitude} \\
        \bitbox{16}{altitude} & \bitbox[lrt]{16}{}
    \end{rightwordgroup} \\
    \begin{leftwordgroup}{Payload}
        \wordbox[lrt]{1}{data} \\
        \skippedwords \\
        \wordbox[lrb]{1}{}
    \end{leftwordgroup}
\end{bytefield}
\end{center}

@@

\newpage
\chapter{Results}
\label{sec:reults}

\newpage
\chapter{Discussion}
\label{sec:discussion}

\newpage
\chapter{Conclusion}
\label{sec:conclusion}

>>>>

\newpage
\chapter{Introduction}
\label{ch:introduction}

\newpage
\chapter{Literature Review}
\label{ch:literature-review}

@@

\newpage
\chapter{Proposed Solution and Methodology}
\label{ch:methodology}

@@

\subsection{Requirements}
\label{ssec:requirements}

@@

As stated in chapter \ref{ch:literature-review}, the United Kingdom's Office
of Communications restrict what frequencies can be used for airborne
radio transmissions, and how much power the transmissions can be sent at.
Those restrictions constrain what existing protocols can be used to transmit
arbitrary data over radio. This disqualifies existing packet radio protocols
that would have fulfilled most of the requirements, in use in other countries
like AX.25.

@@

While RTTY was not considered sufficient to cover fulfil the requirements of
the whole protocol, as shown in section \ref{ssec:requirements}, it fulfils the
simple requirements of the Link Layer: it can be used to send 8-bit bytes, one
by one, over a radio link.

RTTY functions like UART, over radio. Instead of using logical electrical levels
(5V for logical high, 0V for logical low), it uses Audio Frequency Shift Keying
(\textit{AFSK}): two audio tones separated by a frequency shift act as two
logical levels. When nothing is being transmitted, the line is held high. The
start of a byte is signalled by the \textit{start bit} (the line goes low),
followed by the eight \textit{data bits}, and one or two \textit{stop bits} (the
line is held low). After a byte has been sent, the line is held high again until
the next byte, or the next byte starts immediately.

%TODO: replace mentions of UART with RS-232 // NOPE, RS232 diff. than TTL
%TODO: references for DominoEx and Olivia
Other existing protocols exist that can transmit data over radio audio signals,
like DominoEx or Olivia, sometimes with better transmission rates. RTTY was
preferred over them because the ESP8266 board used as OBC in the AHABus
prototype provides hardware support for UART, making it easier to implement and
reliable. Since the link layer is transparent to the frame and packet layers,
RTTY could be swapped for another protocol in the future with no impact on
those.

@@

\begin{figure}[H]
    \begin{bytefield}{16}
        \bitheader{0,7,8,15} \\
        \begin{rightwordgroup}{Header}
            \bitbox{8}{01011010} & \bitbox{8}{version} \\
            \bitbox{16}{sequence number}
        \end{rightwordgroup} \\
        \begin{leftwordgroup}{Payload}
            \wordbox[lrt]{1}{data} \\
            \skippedwords \\
            \wordbox[lrb]{1}{}
        \end{leftwordgroup} \\
        \begin{rightwordgroup}{FEC}
            \wordbox[lrt]{1}{checksum} \\
            \skippedwords \\
            \wordbox[lrb]{1}{}
        \end{rightwordgroup}
    \end{bytefield}
    \centering
    \caption{AHABus Frame Format}
\end{figure}

@@

\begin{figure}[H]
    \begin{bytefield}{32}
        \bitheader{0,7,8,15,16,23,24,31} \\
        \begin{rightwordgroup}{Header}
            \bitbox{8}{version} & \bitbox{8}{payload ID} &
            \bitbox{16}{packet length} \\
            \bitbox{32}{latitude} \\
            \bitbox{32}{longitude} \\
            \bitbox{16}{altitude} & \bitbox[lrt]{16}{}
        \end{rightwordgroup} \\
        \begin{leftwordgroup}{Payload}
            \wordbox[lrt]{1}{data} \\
            \skippedwords \\
            \wordbox[lrb]{1}{}
        \end{leftwordgroup}
    \end{bytefield}
    \centering
    \caption{AHABus Frame Format}
\end{figure}

@@

\newpage
\chapter{Results}
\label{ch:reults}

\newpage
\chapter{Discussion}
\label{ch:discussion}

\newpage
\chapter{Conclusion}
\label{ch:conclusion}
